---
title: "Project"
author: "Simphiwe Mngadi"
date: "10 May 2023"
output: pdf_document
---

```{r}

```
# Luekemia patients
## Description

Christensen (1997) provides data on survival of 33 leukemia patients along with two potential
predictor variables: white blood cell count (measured in thousands of cells per mm3 of blood) and
the existence of a certain morphological characteristic in the cells called AG. If the characteristic is
present the patient is said to be ‘AG positive’ and if it is absent the patient is said to be ‘AG negative.’
The dependent variable is yi as defined below, and the independent variables are xi1 (white blood cell
count) and xi2 as defined below.

yi = {1 if ith patient survived for at least 52 weeks
0 if ith patient died within 52 weeks

xi2 is a binary explanatory variable defined as follows:
xi2 = {1 if the ith patient is AG positive
0 if the ith patient is AG negative.

## fitting the logistic model
```{r}

leukdat <- read.csv("leukemia.csv", header = TRUE)
mylogistic <- glm(Survival ~ CellCount + AG, data = leukdat,
family = binomial(link = logit))
summary(mylogistic)
```

## Statistical significance of coefficients

B2 (AG) is statistically significant at 5% level since the p-value for its significance test is
0.01757 < 0.05 . B1 (CellCount) is not statistically significant since the corresponding p-value
is 0.08814 > 0.05.

## Parameter estimates in practical terms

exp{B1} = exp{3.180 x 10^-2} = 1.032 . This implies that, if white blood cell count increases by
1000 cells per mm3 of blood , the expected odds of a patient surviving leukemia for 52 weeks
decrease by a factor of 1.032. (Or, they change by a factor of 0.9687) .

exp{B2} = exp{2.261} =9.593 . Expected odds of survival for 52 weeks for a leukemia patient whose blood is AG positive
are about 9.593 times as much  as expected odds of survival for 52 weeks for a leukemia patient
whose blood is AG negative  .

# Exposure to chloracetic acid and the death of mice
## Description

Christensen (1997) provides data from experiments conducted to examine the relationship
between exposure to chloracetic acid and the death of mice. Twelve different dose levels were used and
ten mice were exposed at each dose level, yielding a total of 120 observations. Dose level is measured in
grams per kg of body weight.

The dependent variable is defined as follows.

yi= {1 if ith mouse died
0 if ith mouse did not die

## fit the probit regression model
```{r}
aciddat <- read.csv("chloracetic_acid.csv", header = TRUE)
myprobit <- glm(Died ~ Dose, data = aciddat,
family = binomial(link = probit))
summary(myprobit)

```
## sign of the coefficient estimate B1 and explain what this means for the dose-response relationship.

The sign of B1 is positive and B1 is statistically significant at 5% level of significance (p-value is 4.5 × 10^6 < 0.05)  so we can see that as the dose of chloracetic acid increases, the probability of
death for the mouse also increases .

## LD50 and explain what it means.



LD50= -B0/B1= 2.133656/8.745963 = 0.2440. 
We estimate that a dose of 0.2440 g/kg of chloracetic
acid is sufficient to kill a mouse with 50% probability.


## Phat for each of the twelve dose levels represented in the data
```{r}
phat <- unique(myprobit$fitted.values)
yhat <- as.integer(unique(myprobit$fitted.values) >= 0.5)
cbind(phat, yhat)

```

## which dose levels would we predict that a mouse will die, using a threshold value of 0.5?


It would be for dose levels 0.2512, 0.2818, and 0.3162, since these are the dose levels for which phat > 0.5 .
